How Slow do my Transient Typechecks Go?

### 2019-08-17 paper.tex
Fix cite in 0-100 paragraph

By inspecting the scatterplots, we observe that the performance of
Moth in almost any configuration of a benchmark is bounded by
the performance in the untyped and fully-typed configuration.
That is, for these benchmarks on transient type checks,
measuring just the untyped and fully-typed configurations
would provide excellent estimates of a benchmark's
performance bounds.  This is different to the experience
of other kinds of gradual typing, where the best, and most
importantly worst, configurations are not always those
fully typed or fully untyped \cite{greenam-takikiaw-JFP}.
%
However, the Richards and Snake benchmarks \textit{do} have
sections outside these bounds, and isolated executions of
a few others (SpectralNorm, JSON, DeltaBlue) are also outliers.
%
We believe that the 0\% and 100\% bounds are nonetheless a
reasonable heuristic estimator in most cases, and will
examine further the outlying benchmarks.

>>>>

By inspecting the scatterplots, we observe that the performance of
Moth in almost any configuration of a benchmark is bounded by
the performance in the untyped and fully-typed configuration.
That is, for these benchmarks on transient type checks,
measuring just the untyped and fully-typed configurations
would provide excellent estimates of a benchmark's
performance bounds.  This is different to the experience
of other kinds of gradual typing, where the best, and most
importantly worst, configurations are not always those
fully typed or fully untyped \cite{Greenman2019jfp}.
%
However, the Richards and Snake benchmarks \textit{do} have
sections outside these bounds, and isolated executions of
a few others (SpectralNorm, JSON, DeltaBlue) are also outliers.
%
We believe that the 0\% and 100\% bounds are nonetheless a
reasonable heuristic estimator in most cases, and will
examine further the outlying benchmarks.
